---
title: "UN Report Using Markdown"
author: "Zhaohui Fan"
date: "1/12/2021"
output:
  html_document:
    df_print: paged
---

```{r pwd}
getwd()
#setwd("C:/Users/fanluck/Desktop/un-report/data")
```

# R Code chunk
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
library(tidyverse) ## Contain ggplot package
```

This report was prepared to the attention of the United Nations. It analyzes the relationship between a country's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country’s economic strength or weakness may be related to its public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions increase with a country's GDP.

# Read in data
```{r data}
gapminder_1997 <- read_csv("../data/gapminder_data.csv")
```

# GGPLOT to draw the graphs
```{r gdp_lifeexp_1997}
ggplot(data=gapminder_1997)+
 aes(x = gdpPercap, y = lifeExp, color=continent, size=pop/1000000) +
 geom_point() +
 labs(x = "GDP Per Capita", y = "Life Expectancy",
 title= "Do people in wealthy countries live longer?", size="Population (in millions)")
```
